Binary Latent Representations for Efficient Ranking

### 2017-06-14 paper/paper.tex
Elaborate on what scale means. Add pinterest references.

\begin{abstract}
Large-scale recommender systems often face severe latency and storage constraints at prediction time. To relax those, we train recommendation models that use binary rather than real-valued user and item representations, and show that they offer a range of attractive speed-accuracy trade-offs. In particular, we demonstrate 13 times faster prediction at the expense of a modest 4\% loss in ranking accuracy on the Movielens 100K dataset.
\end{abstract}

@@

\section{Introduction}
Industry ranking and recommendation systems need to scale to tens or hundreds of millions of items and users. Ranking latency (in on-line settings) and compute and storage costs (in pre-compute settings) place significant contraints on the design of the resulting system.

In an on-line setting, where recommendation latency directly impacts the user experience, system designers have to work within a strict latency budget. Respecting that budget often means trading off model accuracy for speed, either via smaller and less expressive models (with lower-dimensionality representations) or through aggressive use of heuristics to exclude large classes of candidate items from scoring. For example, approximate nearest neighbour search techniques are used at YouTube \citep{covington2016deep} to reduce the number of candidate videos that need to be scored for each user.

>>>>

\begin{abstract}
Large-scale recommender systems often face severe latency and storage constraints at prediction time. These are particularly acute when the number of items that could be recommended is large, and calculating predictions for the full set is computationally intensive. To relax these constraints, we train recommendation models that use binary rather than real-valued user and item representations, and show that they offer a range of attractive speed-accuracy trade-offs. In particular, we demonstrate 13 times faster prediction at the expense of a modest 4\% loss in ranking accuracy on the Movielens 100K dataset.
\end{abstract}

@@

\section{Introduction}
Industry ranking and recommendation systems need to scale to tens or hundreds of millions of items and users. As the number of items available to be recommended grows large, the challenge of etimating models from large amounts of interaction data is joined by the challenge of efficiently ranking the item catalogue to produce top-ranked recommendations. With large catalogues, ranking latency (in on-line settings) and compute and storage costs (in pre-compute settings) place significant contraints on the design of the entire recommender system.

In an on-line setting, where recommendation latency directly impacts the user experience, system designers have to work within a strict latency budget. Respecting that budget often means trading off model accuracy for speed, either via smaller and less expressive models (with lower-dimensionality representations) or through aggressive use of heuristics to exclude large classes of candidate items from scoring. For example, Pinterest uses a combination of heuristics and candidate-generation models to select approximately 1000 pins, from billions of available pins, as input to its related pins ranking system \citep{liu2017related}. Similarly, approximate nearest neighbour search techniques are used at YouTube \citep{covington2016deep} to reduce the number of candidate videos that need to be scored for each user.
